\newpage
\begin{longtable}{m{2cm}@{\hspace{1cm}}m{11cm}}
\toprule
\textbf{Engagement class} & \textbf{Criteria}\\
\toprule
\textbf{Active} & \begin{itemize}
\item  The comment asks questions or seeks clarification, information or understanding about quantum science \& technology. \item  The comment demonstrates an interest in quantum science \& technology beyond the specific context of the commented article. This includes specific concepts or findings, and broader views on the topic. \item  The comment uses reasoning or evidence to critically evaluates, analyzes or reponds to the content, ideas, or conclusions about quantum science \& technology presented in the commented article. The comment might explicitely cite or implicitely refer to the article content. \item  The comment challenges assumptions or provides alternative perspectives on quantum science \& technology. \item  The comment provides additional context, information, arguments, personal experiences or explanations related to the quantum science \& technology. \item  The comment demonstrates a curiosity or openness to learn more about quantum science \& technology or to discuss the topic further. \item  The comment presents a solution to some problem or suggests a course of action related to quantum science \& technology.
\end{itemize}
\\
\midrule
\textbf{Passive} & \begin{itemize}
    \item  The comment presents a statement of fact or observation about quantum science \& technology without further elaboration or discussion \item  The comment expresses disinterest or apathy towards the topic of quantum science \& technology. \item  The comment expresses frustration, resignation or a lack of understanding on the topic of quantum science \& technology without seeking for clarification or further information. \item  The comment expresses a position (agreement or disagreement) on the commented article without providing any valuable input, reasoning, or evidence. \item  The comment offers no further insights, information or interpretations related to quantum science \& technology beyond the commented article. \item  The comment does not engage at all with the commented article or the topic of quantum science \& technology. It goes off-topic instead.
\end{itemize} \\
\bottomrule 
\caption{Criteria used for categorizing engagement towards quantum science \& technology of comments into 'Active' and 'Passive'.}
\label{tab:annot_crit_engagement}
\end{longtable}
