\afterpage{
\begin{longtable}{m{2cm}@{\hspace{1cm}}m{12cm}}
\toprule
\textbf{Sentiment class} & \textbf{Criteria}\\
\toprule
\textbf{Positive} & \begin{itemize}
\item The comment expresses enthusiasm, optimism, or excitement about quantum science \& technology \item The comment emphasizes or praises the benefits of quantum science \& technology. \item The comment suggests that quantum science \& technology has a value or is an improvement for a specific field/sector. \item The comment states that quantum science \& technology has an advantage compared to something else (e.g. faster, safer, ...)
\end{itemize}
\\
\midrule
\textbf{Neutral} & \begin{itemize}
   \item The comment expresses agreement/disagreement with, or provides feedback on, the commented article without expressing any clear positive or negative sentiment towards quantum science \& technology. \item The comment presents information or facts without expressing any clear positive or negative sentiment towards quantum science \& technology. \item The comment asks questions or seeks clarification about quantum science \& technology without expressing any clear positive or negative sentiment towards the topic. \item The comment acknowledges quantum science \& technology without expressing any clear positive or negative sentiment towards the topic.
\end{itemize} \\
\midrule
\textbf{Negative} & \begin{itemize}
   \item The comment expresses concern, worry, or skepticism about quantum science \& technology. \item The comment expresses frustration or disappointment with the current state of quantum science \& technology. \item The comment discusses potential negative consequences or risks associated with the use of quantum science \& technology. \item The comment suggests that quantum science \& technology is a step backwards or a problem for a specific field/sector. \item The comment states that quantum science \& technology has a disadvantage compared to something else.
\end{itemize} \\
\bottomrule 
\caption{Criteria used for categorizing sentiment towards quantum science \& technology of comments into 'Active' and 'Passive'.}
\label{tab:annot_crit_sentiment}
\end{longtable}
}